---
title: "Team 6 Project Proposal"
subtitle: 'Math 268: Data Analysis and Visualization'
author: 'Joseph Linneman, Theo Mandelbaum, Rose Villareale'
date: "Due 11/7/2025"
output:
  html_document:
    highlight: espresso
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: yes
    fig_caption: true
    df_print: tibble
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,   
  message = FALSE
)
```


```{r echo=FALSE}
library(tidyverse)
library(here)

```


### Project Idea/Research Question

How strongly does air quality / pollution contribute to risk of chronic respiratory illness?

#### Followup Questions

- How much more at risk are urban citizens in this context?
- What are some of the most dangerous counties to live in, regarding these factors?
- How has air quality worsened or improved over time and how has that affected chronic illness rates?



### Data and Data Source

#### Data on Chronic Disease Infection

[Link to Dataset](https://catalog.data.gov/dataset/u-s-chronic-disease-indicators)


#### Data on National Air Quality Metrics
[Link to Dataset](https://catalog.data.gov/dataset/air-quality-measures-on-the-national-environmental-health-tracking-network)



### Anticipated Results

### Member Contributions



